NFC and burnout in teachers - A replication and extension study

### 2021-08-31 Manuscript/Manuscript.Rmd
plot looks better

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)

@@

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 7, edge.label.cex = 0.8, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       theme = "colorblind" # select appropriate colour scheme
                       )
```

>>>>

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)
library(qgraph)

@@

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Burnout", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 0.8, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       theme = "colorblind" # select appropriate colour scheme
                       )
```
